---
title: "inovick_OriginalHomeworkCode_03"
output: html_document
---
## Loading the data
```{r}
library("curl")
library("ggplot2")
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
summary(d)
#getting the data from github using curl
```

##Challenge 1: Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education). NOTE: You will not want to use the built in var() and sd() commands as these are for samples. 
```{r}
##Calculating population mean for height, weight, age, number of zombies killed, and years of education
mean(d$height) #67.6301
mean(d$weight) #143.9075
mean(d$age) #20.04696
mean(d$zombies_killed) #2.992
mean(d$years_of_education) #2.996

##Calculating population SD for height, weight, age, number of zombies killed, and years of education
##Found on stack overflow lol
x <- d$height
sdp <- function(x) sqrt(mean((x-mean(x))^2))
sdp(x) #4.30797

x <- d$weight
sdp <- function(x) sqrt(mean((x-mean(x))^2))
sdp(x) #18.39186

x <- d$age
sdp <- function(x) sqrt(mean((x-mean(x))^2))
sdp(x) #2.963583

x <- d$zombies_killed
sdp <- function(x) sqrt(mean((x-mean(x))^2))
sdp(x) #1.747551

x <- d$years_of_education
sdp <- function(x) sqrt(mean((x-mean(x))^2))
sdp(x) #1.675704
```
##Challenge 2: Use {ggplot} to make boxplots of each of these variables by gender. Not sure why they are on top of each other? Did I switch up the axes?
#Height:
```{r}
p <- ggplot(data = d, aes(x = height, y = gender))
p <- p + geom_boxplot()
p
```

#Weight
```{r}
p <- ggplot(data = d, aes(x = weight, y = gender))
p <- p + geom_boxplot()
p
```

#Age
```{r}
p <- ggplot(data = d, aes(x = age, y = gender))
p <- p + geom_boxplot()
p
```

#Zombie Killed
```{r}
p <- ggplot(data = d, aes(x = zombies_killed, y = gender))
p <- p + geom_boxplot()
p
```

#Years of education
```{r}
p <- ggplot(data = d, aes(x = years_of_education, y = gender))
p <- p + geom_boxplot()
p
```

##Challenge 3: Use {ggplot} to make scatterplots of height and weight in relation to age. Do these variables seem to be related? In what way?
```{r}
attach(d)
par(mfrow = c(1, 2))
plot(x = age, y = height)
plot(x = age, y = weight)
#These variables do seem related. As an individual increases in age, they also increase in height and weight. However, weight does not have as strong a relationship to age as height does. Neither of them have an incredibly strong relationship but there is a positive trend.
```