---
title: "inovick_OriginalHomeworkCode_03"
output: html_document
---
## Loading the data
```{r}
library("curl")
library("ggplot2")
install.packages("Rmisc")
install.packages("manipulate")
library(Rmisc)
library(manipulate)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
summary(d)
#getting the data from github using curl
```
### Summary of challenges: This homework was really tough for me! Even though I looked through all the modules, did the modules, googled, and had help from my peers during a group zoom meeting. I think I am used to finding the actual code for what I need, and not needing to adjust it as much, so that has made things tricky. I know this is a part of the learning process!

##Challenge 1: Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education). NOTE: You will not want to use the built in var() and sd() commands as these are for samples. 

##Calculating population mean for height, weight, age, number of zombies killed, and years of education
```{r}
mean(d$height) #67.6301
mean(d$weight) #143.9075
mean(d$age) #20.04696
mean(d$zombies_killed) #2.992
mean(d$years_of_education) #2.996
```
##Calculating population SD for height, weight, age, number of zombies killed, and years of education
```{r}
sdp <- function(x) sqrt(mean((x-mean(x))^2)) #I created this function so I wouldn't have to do it for ever variable each time. Thanks, Diego!

h <- d$height
sdp(h) #4.30797

w <- d$weight
sdp(w) #18.39186

a <- d$age
sdp(a) #2.963583

z <- d$zombies_killed
sdp(z) #1.747551

e <- d$years_of_education
sdp(e) #1.675704
```
##Challenge 2: Use {ggplot} to make boxplots of each of these variables by gender. 
#Height:
```{r}
p <- ggplot(data = d, aes(x = gender, y = height))
p <- p + geom_boxplot()
p
```

#Weight
```{r}
p <- ggplot(data = d, aes(x = gender, y = weight))
p <- p + geom_boxplot()
p
```

#Age
```{r}
p <- ggplot(data = d, aes(x = gender, y = age))
p <- p + geom_boxplot()
p
```

#Zombies Killed
```{r}
p <- ggplot(data = d, aes(x = gender, y = zombies_killed))
p <- p + geom_boxplot()
p
```

#Years of education
```{r}
p <- ggplot(data = d, aes(x = gender, y = years_of_education))
p <- p + geom_boxplot()
p
```

##Challenge 3: Use {ggplot} to make scatterplots of height and weight in relation to age. Do these variables seem to be related? In what way?
```{r}
height_age <- ggplot(d, aes(age, height)) + geom_point(color = "chartreuse") + xlab("Age") + ylab("Height") + geom_smooth(method = lm) 
height_age

weight_age <- ggplot(d, aes(age, weight)) + geom_point(color = "blueviolet") + xlab("Age") + ylab("Weight") + geom_smooth(method = lm)
weight_age
#These variables do seem related. As an individual increases in age, they also increase in height and weight. However, weight does not have as strong a relationship to age as height does. Neither of them have an incredibly strong relationship but there is a positive trend.
```

##Challenge 4: Using histograms and Q-Q plots, check whether the quantitative variables seem to be drawn from a normal distribution. Which seem to be and which do not (hint: not all are drawn from the normal distribution)? For those that are not normal, can you determine from which common distribution they are drawn? 
```{r}
hist(d$height) #normal
qqnorm(d$height)

hist(d$weight) #normal
qqnorm(d$weight)

hist(d$age) #normal
qqnorm(d$age)

hist(d$zombies_killed)#skewed-- poisson
qqnorm(d$zombies_killed)

hist(d$years_of_education) #skewed-- poisson
qqnorm(d$years_of_education)


#I looked at both the histograms and Q-Qplots to determine this. I kept getting an error when using qqline saying that I had not called the plot yet.
```

##Challenge 5: Now use the sample() function to sample ONE subset of 30 zombie survivors (without replacement) from this population and calculate the mean and sample standard deviation for each variable. Also estimate the standard error for each variable, and construct the 95% confidence interval for each mean. Note that for the variables that are not drawn from the normal distribution, you may need to base your estimate of the CIs on slightly different code than for the normal… 
```{r}
#height
sample_height <- sample(d$height, size = 30, replace = FALSE, prob = NULL) #separate by variable
mean(sample_height) #67.43253
sd(sample_height) #4.622798

#weight
sample_weight <- sample(d$weight, size = 30, replace = FALSE, prob = NULL)
mean(sample_weight) #147.273
sd(sample_weight) #17.2789

#age
sample_age <- sample(d$age, size = 30, replace = FALSE, prob = NULL)
mean(sample_age) #20.27081
sd(sample_age) #3.06221

#zombies killed
sample_zombies_killed <- sample(d$zombies_killed, size = 30, replace = FALSE, prob = NULL)
mean(sample_zombies_killed) #2.766667
sd(sample_zombies_killed) #1.633345

#years of education
sample_education <- sample(d$years_of_education, size = 30, replace = FALSE, prob = NULL)
mean(sample_education) #2.933333
sd(sample_education) #1.740657
```

## Confidence intervals: Age
```{r}
x <- sample_age
m <- mean(x)
normalCI = function(x, CIlevel = 0.95) {
    upper = m + qnorm(1 - (1 - CIlevel)/2) * sqrt(var(x)/length(x))
    lower = m + qnorm((1 - CIlevel)/2) * sqrt(var(x)/length(x))
    ci <- c(lower, upper)
    return(ci)
}
normalCI(x=sample_age, 0.95)
```
## Confidence intervals: Weight
```{r}
x <- sample_weight
m <- mean(x)
normalCI = function(x, CIlevel = 0.95) {
    upper = m + qnorm(1 - (1 - CIlevel)/2) * sqrt(var(x)/length(x))
    lower = m + qnorm((1 - CIlevel)/2) * sqrt(var(x)/length(x))
    ci <- c(lower, upper)
    return(ci)
}
normalCI(x=sample_weight, 0.95)
```
##Confidence intervals: Height
```{r}
x <- sample_height
m <- mean(x)
normalCI = function(x, CIlevel = 0.95) {
    upper = m + qnorm(1 - (1 - CIlevel)/2) * sqrt(var(x)/length(x))
    lower = m + qnorm((1 - CIlevel)/2) * sqrt(var(x)/length(x))
    ci <- c(lower, upper)
    return(ci)
}
normalCI(x=sample_height, 0.95)
```
##Confidence Intervals: Zombies killed and years of education. Since this isn't a normal distribution, we are basing it off of a Poisson distribution
```{r}
set.seed(1)
s <- sample(1:nrow(d), 30, replace = F)
d[s,] #To sample 30 people

m_age <- mean(d$age[s])
m_age
m_zk <- mean(d$zombies_killed[s])
m_zk
m_yoe <- mean(d$years_of_education[s])
m_yoe #Calculating the sample mean of zombies killed and years of education

sd(d$zombies_killed[s])
sd(d$years_of_education[s]) #Calculating the standard deviation of zombies killed and years of education


## Function to calculate standard error
se <- function(x) {
    sd(x)/sqrt(length(x))
}

se_zk <- se(d$zombies_killed[s])
se_zk
se_yoe <- se(d$years_of_education[s])
se_yoe #Calculating standard error of zombies killed and years of education

#For lambda we used population mean from question 1
lower_zk <- m_zk - qpois(1 - 0.05/2, 2.992) * se_zk
upper_zk <- m_zk + qpois(1 - 0.05/2, 2.992) * se_zk
ci_zk <- c(lower_zk, upper_zk)
ci_zk #95% CI for zombies killed

lower_yoe <- m_yoe - qpois(1 - 0.05/2, 2.996) * se_yoe
upper_yoe <- m_yoe + qpois(1 - 0.05/2, 2.996) * se_yoe
ci_yoe <- c(lower_yoe, upper_yoe)
ci_yoe #95% CI for years of education
```

##Challenge 6:Now draw 99 more random samples of 30 zombie apocalypse survivors, and calculate the mean for each variable for each of these samples. Together with the first sample you drew, you now have a set of 100 means for each variable (each based on 30 observations), which constitutes a sampling distribution for each variable. What are the means and standard deviations of this distribution of means for each variable? How do the standard deviations of means compare to the standard errors estimated in [5]? What do these sampling distributions look like (a graph might help here)? Are they normally distributed? What about for those variables that you concluded were not originally drawn from a normal distribution? 
```{r}
#Modified Diego's code (with permission)-- Thank you Diego!
#age
f <- NULL
for (i in 1:99) {
    f[[i]] <- sample(1:nrow(d), size = 30, replace = FALSE)
}
#To check the sampling
d[f[[1]],]

## This code calculates the mean for each variable of each sample
mh <- NULL
for (i in 1:99) {
    mh[i] <- mean(d$height[f[[i]]])
}
mw <- NULL
for (i in 1:99) {
    mw[i] <- mean(d$weight[f[[i]]])
}
mzk <- NULL
for (i in 1:99) {
    mzk[i] <- mean(d$zombies_killed[f[[i]]])
}
myoe <- NULL
for (i in 1:99) {
    myoe[i] <- mean(d$years_of_education[f[[i]]])
}
ma <- NULL
for (i in 1:99) {
    ma[i] <- mean(d$age[f[[i]]])
}


## This calculates the mean of the means of the 100 samples (this 99 and the previous one from question 5)
m_age <- mean(d$age[s])
m_age

meanasamp <- c(ma,m_age) #age

m_weight <- mean(d$weight[s])
m_weight

meanwsamp <- c(m,m_weight) #weight

m_height <- mean(d$height[s])
m_height

meanhsamp <- c(mw,m_height) #height

m_zk <- mean(d$zombies_killed[s])
m_zk

meanzksamp <- c(mzk,m_zk) #zombies killed

m_education <- mean(d$years_of_education[s])
m_education

meanedsamp <- c(myoe,m_education) #years of education


mean(meanhsamp)
mean(meanwsamp)
mean(meanzksamp)
mean(meanedsamp)
mean(meanasamp)

## This calculates the standard deviation of the means of the 100 samples (this 99 and the previous one from question 5)
sd(meanhsamp)
sd(meanwsamp)
sd(meanzksamp)
sd(meanedsamp)
sd(meanasamp)

## When comparing with the standard errors estimated before, they are really close
se_height <- se(d$height[s])
se_height
se_weight <- se(d$weight[s])
se_weight
se_zk <- se(d$zombies_killed[s])
se_zk
se_yoe <- se(d$years_of_education[s])
se_yoe
se_age <- se(d$age[s])

se_age
se_height
se_weight
se_zk
se_yoe
se_age

hist(meanhsamp)
hist(meanwsamp)
hist(meanzksamp)
hist(meanedsamp)
hist(meanasamp)

#All are normally distributed even though they aren't all from a normal distribution originally
```
