---
title: "inovick_OriginalHomeworkCode_03"
output: html_document
---
## Loading the data
```{r}
library("curl")
library("ggplot2")
install.packages("Rmisc")
install.packages("manipulate")
library(Rmisc)
library(manipulate)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
summary(d)
#getting the data from github using curl
```
### Summary of challenges: This homework was really tough for me! Even though I looked through all the modules, did the modules, googled, and had help from my peers during a group zoom meeting. I think I am used to finding the actual code for what I need, and not needing to adjust it as much, so that has made things tricky. I know this is a part of the learning process!

##Challenge 1: Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education). NOTE: You will not want to use the built in var() and sd() commands as these are for samples. 

##Calculating population mean for height, weight, age, number of zombies killed, and years of education
```{r}
mean(d$height) #67.6301
mean(d$weight) #143.9075
mean(d$age) #20.04696
mean(d$zombies_killed) #2.992
mean(d$years_of_education) #2.996
```
##Calculating population SD for height, weight, age, number of zombies killed, and years of education
```{r}
sdp <- function(x) sqrt(mean((x-mean(x))^2)) #I created this function so I wouldn't have to do it for ever variable each time. Thanks, Diego!

h <- d$height
sdp(h) #4.30797

w <- d$weight
sdp(w) #18.39186

a <- d$age
sdp(a) #2.963583

z <- d$zombies_killed
sdp(z) #1.747551

e <- d$years_of_education
sdp(e) #1.675704
```
##Challenge 2: Use {ggplot} to make boxplots of each of these variables by gender. 
#Height:
```{r}
p <- ggplot(data = d, aes(x = gender, y = height))
p <- p + geom_boxplot()
p
```

#Weight
```{r}
p <- ggplot(data = d, aes(x = gender, y = weight))
p <- p + geom_boxplot()
p
```

#Age
```{r}
p <- ggplot(data = d, aes(x = gender, y = age))
p <- p + geom_boxplot()
p
```

#Zombies Killed
```{r}
p <- ggplot(data = d, aes(x = gender, y = zombies_killed))
p <- p + geom_boxplot()
p
```

#Years of education
```{r}
p <- ggplot(data = d, aes(x = gender, y = years_of_education))
p <- p + geom_boxplot()
p
```

##Challenge 3: Use {ggplot} to make scatterplots of height and weight in relation to age. Do these variables seem to be related? In what way?
```{r}
height_age <- ggplot(d, aes(age, height)) + geom_point(color = "chartreuse") + xlab("Age") + ylab("Height") + geom_smooth(method = lm) 
height_age

weight_age <- ggplot(d, aes(age, weight)) + geom_point(color = "blueviolet") + xlab("Age") + ylab("Weight") + geom_smooth(method = lm)
weight_age
#These variables do seem related. As an individual increases in age, they also increase in height and weight. However, weight does not have as strong a relationship to age as height does. Neither of them have an incredibly strong relationship but there is a positive trend.
```

##Challenge 4: Using histograms and Q-Q plots, check whether the quantitative variables seem to be drawn from a normal distribution. Which seem to be and which do not (hint: not all are drawn from the normal distribution)? For those that are not normal, can you determine from which common distribution they are drawn? 
```{r}
hist(d$height) #normal
qqnorm(d$height)
qqline(d$height)

hist(d$weight) #normal


hist(d$age) #normal


hist(d$zombies_killed) #skewed-- poisson


hist(d$years_of_education) #skewed-- poisson


#I just looked at the histograms to determine this. I am sure there is a better way to determine type of distribution, but this seemed like the most straightforward way?
```

##Challenge 5: Now use the sample() function to sample ONE subset of 30 zombie survivors (without replacement) from this population and calculate the mean and sample standard deviation for each variable. Also estimate the standard error for each variable, and construct the 95% confidence interval for each mean. Note that for the variables that are not drawn from the normal distribution, you may need to base your estimate of the CIs on slightly different code than for the normal… 
```{r}
#height
sample_height <- sample(d$height, size = 30, replace = FALSE, prob = NULL) #separate by variable
mean(sample_height) #67.43253
sd(sample_height) #4.622798

#weight
sample_weight <- sample(d$weight, size = 30, replace = FALSE, prob = NULL)
mean(sample_weight) #147.273
sd(sample_weight) #17.2789

#age
sample_age <- sample(d$age, size = 30, replace = FALSE, prob = NULL)
mean(sample_age) #20.27081
sd(sample_age) #3.06221

#zombies killed
sample_zombies_killed <- sample(d$zombies_killed, size = 30, replace = FALSE, prob = NULL)
mean(sample_zombies_killed) #2.766667
sd(sample_zombies_killed) #1.633345

#years of education
sample_education <- sample(d$years_of_education, size = 30, replace = FALSE, prob = NULL)
mean(sample_education) #2.933333
sd(sample_education) #1.740657

x <- sample_age
m <- mean(x)
normalCI = function(x, CIlevel = 0.95) {
    upper = m + qnorm(1 - (1 - CIlevel)/2) * sqrt(var(x)/length(x))
    lower = m + qnorm((1 - CIlevel)/2) * sqrt(var(x)/length(x))
    ci <- c(lower, upper)
    return(ci)
}
normalCI(x=mean(sample_age), 0.95)
#I am STRUGGLING with this. I keep getting N/A as my answers. Am I doing something that's canceling out? Help lmao

#Do I use this instead?
set <- NULL  # sets up a dummy variable to hold our 10000 simulations
n <- 15
for (i in 1:10000) {
    set[i] <- mean(sample(x, n, replace = TRUE))
} #and also material from module 8?
```

##Challenge 6:Now draw 99 more random samples of 30 zombie apocalypse survivors, and calculate the mean for each variable for each of these samples. Together with the first sample you drew, you now have a set of 100 means for each variable (each based on 30 observations), which constitutes a sampling distribution for each variable. What are the means and standard deviations of this distribution of means for each variable? How do the standard deviations of means compare to the standard errors estimated in [5]? What do these sampling distributions look like (a graph might help here)? Are they normally distributed? What about for those variables that you concluded were not originally drawn from a normal distribution? 
```{r}
#From module 7- interesting questions to ask
#Do it without replacement
#Sample 100 times

for (n in seq(5, 50, 5)) # samples of 5, 10, 15... for (n in seq(5, 50,
for (n in seq(5, 50, 5)) # samples of 5, 10, 15... 5)) # samples of 5, 10,
for (n in seq(5, 50, 5)) # samples of 5, 10, 15... 15...
{
    for (i in 1:50) # 50 replicates for (i in 1:50) # 50 replicates
    {
        x <- rnorm(n, mean = 10, sd = 2)
        points(n, var(x))
    }
}

#From module 8
k <- 1000  # number of samples
n <- 5  # size of each sample
s <- NULL  # dummy variable to hold each sample
for (i in 1:k) {
    s[[i]] <- sample(x, size = n, replace = FALSE)
}
head(s)
```
