---
title: "inovick_OriginalHomeworkCode_03"
output: html_document
---
## Loading the data
```{r}
library("curl")
library("ggplot2")
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
summary(d)
#getting the data from github using curl
```

##Challenge 1: Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education). NOTE: You will not want to use the built in var() and sd() commands as these are for samples. 
```{r}
##Calculating population mean for height, weight, age, number of zombies killed, and years of education
mean(d$height) #67.6301
mean(d$weight) #143.9075
mean(d$age) #20.04696
mean(d$zombies_killed) #2.992
mean(d$years_of_education) #2.996

##Calculating population SD for height, weight, age, number of zombies killed, and years of education
##Found on stack overflow lol
x <- d$height
sdp <- function(x) sqrt(mean((x-mean(x))^2))
sdp(x) #4.30797

x <- d$weight
sdp <- function(x) sqrt(mean((x-mean(x))^2))
sdp(x) #18.39186

x <- d$age
sdp <- function(x) sqrt(mean((x-mean(x))^2))
sdp(x) #2.963583

x <- d$zombies_killed
sdp <- function(x) sqrt(mean((x-mean(x))^2))
sdp(x) #1.747551

x <- d$years_of_education
sdp <- function(x) sqrt(mean((x-mean(x))^2))
sdp(x) #1.675704
```

# You can use the SummarySE function in the package Rmisc to do all of the summary statistics for you

##Challenge 2: Use {ggplot} to make boxplots of each of these variables by gender. Not sure why they are on top of each other? Did I switch up the axes?
#Height:
```{r}
p <- ggplot(data = d, aes(x = height, y = gender))
p <- p + geom_boxplot()
p

```

#Weight
```{r}
p <- ggplot(data = d, aes(x = weight, y = gender))
p <- p + geom_boxplot()
p
```

#Age
```{r}
p <- ggplot(data = d, aes(x = age, y = gender))
p <- p + geom_boxplot()
p
```

#Zombie Killed
```{r}
p <- ggplot(data = d, aes(x = zombies_killed, y = gender))
p <- p + geom_boxplot()
p
```

#Years of education
```{r}
p <- ggplot(data = d, aes(x = years_of_education, y = gender))
p <- p + geom_boxplot()
p
```

##Challenge 3: Use {ggplot} to make scatterplots of height and weight in relation to age. Do these variables seem to be related? In what way?
```{r}
attach(d)
par(mfrow = c(1, 2))
plot(x = age, y = height)
plot(x = age, y = weight)
#These variables do seem related. As an individual increases in age, they also increase in height and weight. However, weight does not have as strong a relationship to age as height does. Neither of them have an incredibly strong relationship but there is a positive trend.
```

# you can use ggplot to create a more aesthetically pleasing graph with the functions geom_point() and geom_line()


##Challenge 4: Using histograms and Q-Q plots, check whether the quantitative variables seem to be drawn from a normal distribution. Which seem to be and which do not (hint: not all are drawn from the normal distribution)? For those that are not normal, can you determine from which common distribution they are drawn? 
```{r}
hist(d$height) #normal
hist(d$weight) #normal
hist(d$age) #normal
hist(d$zombies_killed) #skewed-- poisson
hist(d$years_of_education) #skewed-- poisson
#I just looked at the histograms to determine this. I am sure there is a better way to determine type of distribution, but this seemed like the most straightforward way?

# looks great!

```

##Challenge 5: Now use the sample() function to sample ONE subset of 30 zombie survivors (without replacement) from this population and calculate the mean and sample standard deviation for each variable. Also estimate the standard error for each variable, and construct the 95% confidence interval for each mean. Note that for the variables that are not drawn from the normal distribution, you may need to base your estimate of the CIs on slightly different code than for the normal… 
```{r}
#height
sample_height <- sample(d$height, size = 30, replace = FALSE, prob = NULL) #separate by variable
mean(sample_height) #67.43253
sd(sample_height) #4.622798

#weight
sample_weight <- sample(d$weight, size = 30, replace = FALSE, prob = NULL)
mean(sample_weight) #147.273
sd(sample_weight) #17.2789

#age
sample_age <- sample(d$age, size = 30, replace = FALSE, prob = NULL)
mean(sample_age) #20.27081
sd(sample_age) #3.06221

#zombies killed
sample_zombies_killed <- sample(d$zombies_killed, size = 30, replace = FALSE, prob = NULL)
mean(sample_zombies_killed) #2.766667
sd(sample_zombies_killed) #1.633345

#years of education
sample_education <- sample(d$years_of_education, size = 30, replace = FALSE, prob = NULL)
mean(sample_education) #2.933333
sd(sample_education) #1.740657

x <- sample_age
m <- mean(x)
normalCI = function(x, CIlevel = 0.95) {
    upper = m + qnorm(1 - (1 - CIlevel)/2) * sqrt(var(x)/length(x))
    lower = m + qnorm((1 - CIlevel)/2) * sqrt(var(x)/length(x))
    ci <- c(lower, upper)
    return(ci)
}
normalCI(x=mean(sample_age), 0.95)
#I am STRUGGLING with this. I keep getting N/A as my answers. Am I doing something that's canceling out? Help lmao

# I don't really think a function is necessary but I hear Diego has corrected it which is great


#Do I use this instead?
set <- NULL  # sets up a dummy variable to hold our 10000 simulations
n <- 15
for (i in 1:10000) {
    set[i] <- mean(sample(x, n, replace = TRUE))
} #and also material from module 8?


# Also a loop is not necessary here


```

##Challenge 6:Now draw 99 more random samples of 30 zombie apocalypse survivors, and calculate the mean for each variable for each of these samples. Together with the first sample you drew, you now have a set of 100 means for each variable (each based on 30 observations), which constitutes a sampling distribution for each variable. What are the means and standard deviations of this distribution of means for each variable? How do the standard deviations of means compare to the standard errors estimated in [5]? What do these sampling distributions look like (a graph might help here)? Are they normally distributed? What about for those variables that you concluded were not originally drawn from a normal distribution? 
```{r}
#From module 7- interesting questions to ask
#Do it without replacement
#Sample 100 times

for (n in seq(5, 50, 5)) # samples of 5, 10, 15... for (n in seq(5, 50,
for (n in seq(5, 50, 5)) # samples of 5, 10, 15... 5)) # samples of 5, 10,
for (n in seq(5, 50, 5)) # samples of 5, 10, 15... 15...
{
    for (i in 1:50) # 50 replicates for (i in 1:50) # 50 replicates
    {
        x <- rnorm(n, mean = 10, sd = 2)
        points(n, var(x))
    }
}

# You need a null variable to put the output in
# an "i" the 99 times you run the code
# and a mean(sample(...)) function to make the code output
# Here is my code

# x_height <- NULL
# for (i in 1:99) {
#   x_height[i] <- mean(sample(d$height, size = 30, replace = FALSE)) 
#  }



#From module 8
k <- 1000  # number of samples
n <- 5  # size of each sample
s <- NULL  # dummy variable to hold each sample
for (i in 1:k) {
    s[[i]] <- sample(x, size = n, replace = FALSE)
}
head(s)
```